\bibitem{ReID3D}
Guo W, Pan Z, Liang Y, et al. LiDAR-based person re-identification. In: Proceedings of the IEEE/CVF Conference on Computer Vision and Pattern Recognition (CVPR); 2024 Jun 17--21; Seattle, WA. Los Alamitos (CA): IEEE Computer Society; 2024. p. 17437--17447.

\bibitem{2D LiDAR}
Arras KO, Mozos OM, Burgard W. Using boosted features for the detection of people in 2D range data. In: Proceedings of the IEEE International Conference on Robotics and Automation (ICRA); 2007 Apr 10--14; Rome, Italy. Piscataway (NJ): IEEE; 2007. p. 3402--3407.

\bibitem{3D LiDAR}
Yan Z, Duckett T, Bellotto N. Online learning for 3D LiDAR-based human detection: experimental analysis of point cloud clustering and classification methods. Auton Robot. 2020;44:147--164.

\bibitem{Monocular}
Koide K, Miura J, Menegatti E. Monocular person tracking and identification with on-line deep feature selection for person following robots. Robot Auton Syst. 2020;124:103348.

\bibitem{Camera LiDAR}
Krebs S, Gavrila DM. Camera- and LiDAR-based person re-identification. In: Proceedings of the IEEE Intelligent Vehicles Symposium (IV); 2025 Jun 22--25; Cluj-Napoca, Romania. Piscataway (NJ): IEEE; 2025. p. 1408--1414.

\bibitem{PointPillars}
Lang AH, Vora S, Caesar H, et al. PointPillars: fast encoders for object detection from point clouds. In: Proceedings of the IEEE/CVF Conference on Computer Vision and Pattern Recognition (CVPR); 2019 Jun 16--20; Long Beach, CA. Los Alamitos (CA): IEEE Computer Society; 2019. p. 12697--12705.

\bibitem{KITTI}
Geiger A, Lenz P, Urtasun R. Are we ready for autonomous driving? The KITTI vision benchmark suite. In: Proceedings of the IEEE/CVF Conference on Computer Vision and Pattern Recognition (CVPR); 2012 Jun 16--21; Providence, RI. Los Alamitos (CA): IEEE Computer Society; 2012. p. 3354--3361.

\bibitem{3D BAT}
Zimmer W, Rangesh A, Trivedi M. 3D BAT: a semi-automatic, web-based 3D annotation toolbox for full-surround, multi-modal data streams. In: Proceedings of the IEEE Intelligent Vehicles Symposium (IV); 2019 Jun 9--12; Paris, France. Piscataway (NJ): IEEE; 2019. p. 583--590.

\bibitem{TPT-Bench}
Ye H, Zhan Y, Situ W, et al. TPT-Bench: a large-scale, long-term and robot-egocentric dataset for benchmarking target person tracking. arXiv preprint arXiv:2505.07446 [Internet]. 2025 [cited 2026 Jan 18]. Available from: https://arxiv.org/abs/2505.07446

\bibitem{JRDB-PanoTrack}
Martin-Martin R, Patel M, Rezatofighi H, et al. JRDB-PanoTrack: an open-world panoptic segmentation and tracking robotic dataset in crowded human environments. In: Proceedings of the IEEE/CVF Conference on Computer Vision and Pattern Recognition (CVPR); 2024 Jun 17--21; Seattle, WA. Los Alamitos (CA): IEEE Computer Society; 2024. p. 22325--22334.

\bibitem{RobSense}
Do MK, Han K, Lai P, et al. RobSense: a robust multi-modal foundation model for remote sensing with static, temporal, and incomplete data adaptability. In: Proceedings of the IEEE/CVF Conference on Computer Vision and Pattern Recognition (CVPR); 2025 Jun 11--15; Nashville, TN. Los Alamitos (CA): IEEE Computer Society; 2025. p. 7427--7436.

\bibitem{SiamRPN++}
Li B, Wu W, Wang Q, et al. SiamRPN++: evolution of Siamese visual tracking with very deep networks. In: Proceedings of the IEEE/CVF Conference on Computer Vision and Pattern Recognition (CVPR); 2019 Jun 16--20; Long Beach, CA. Los Alamitos (CA): IEEE Computer Society; 2019. p. 4282--4291.

\bibitem{DiMP}
Bhat G, Danelljan M, Van Gool L, et al. Learning discriminative model prediction for tracking. In: Proceedings of the IEEE/CVF International Conference on Computer Vision (ICCV); 2019 Oct 27--Nov 2; Seoul, Korea. Los Alamitos (CA): IEEE Computer Society; 2019. p. 6182--6191.

\bibitem{MixFormer}
Cui Y, Jiang C, Wang L, et al. MixFormer: end-to-end tracking with iterative mixed attention. In: Proceedings of the IEEE/CVF Conference on Computer Vision and Pattern Recognition (CVPR); 2022 Jun 19--24; New Orleans, LA. Los Alamitos (CA): IEEE Computer Society; 2022. p. 13608--13618.

\bibitem{OCL-RPF}
Ye H, Zhao J, Zhan Y, et al. Person re-identification for robot person following with online continual learning. IEEE Robot Autom Lett. 2024;9(11):9151--9158.